HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-07-03 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Update pomodoro time

Another challenge is the wide heterogeneity in
student competence. Special care must be given to setup
a training structure that can cope with both beginners and advanced students.
This may rest on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrict their tutorials to 20 minutes
of material, as inspired by the Pomodoro technique\cite{PomodoroTechnique}, so
that one can easily jump and compose one's own ``menu''. However, it turns out to be tricky to keep such
small tutorials really independant and meaningful when they can be selected at
will.

>>>>

Another challenge is the wide heterogeneity in
student competence. Special care must be given to setup
a training structure that can cope with both beginners and advanced students.
This may rest on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrict their tutorials to 25 minutes
of material, as inspired by the Pomodoro technique\cite{PomodoroTechnique}, so
that one can easily jump and compose one's own ``menu''. However, it turns out to be tricky to keep such
small tutorials really independant and meaningful when they can be selected at
will.
